### 2021-06-09 paper/report.tex
Position note outside footnote...

The largest effect---almost one half when considering the decompositions---comes from
rapid testing. Here, it is crucial to differentiate between recorded cases and actual
cases. Additional testing means that infections become known which would otherwise
remain undetected. Figure~\ref{fig:2021_scenarios_recorded} shows that this means that
until late April, recorded cases are higher than in the scenario where none of the three
mechanisms is turned on. Compared to the scenario with vaccinations only, this point is
reached only around mid May and it would be June for the comparison with the
seasonality-only scenario. The effect on total cases, however, is visible immediately.
Despite the fact that only a small fraction of the population performed weekly rapid
tests in March\footnote{X\%\comment[id=HM]{Put in}in the model; 27\% of respondents to
the COSMO study reported in early March that they \textit{ever} did a rapid test)}, new
infections on April 1 would be rise in new infections would be reduced by 53\% relative
to the scenario without vaccinations, rapid tests, or seasonality.

>>>>

The largest effect---almost one half when considering the decompositions---comes from
rapid testing. Here, it is crucial to differentiate between recorded cases and actual
cases. Additional testing means that infections become known which would otherwise
remain undetected. Figure~\ref{fig:2021_scenarios_recorded} shows that this means that
until late April, recorded cases are higher than in the scenario where none of the three
mechanisms is turned on. Compared to the scenario with vaccinations only, this point is
reached only around mid May and it would be June for the comparison with the
seasonality-only scenario. The effect on total cases, however, is visible immediately.
Despite the fact that only a small fraction of the population performed weekly rapid
tests in March\footnote{X\% in the model; 27\% of respondents to the COSMO study
reported in early March that they \textit{ever} did a rapid test)}\comment[id=HM]{Put
in}, new infections on April 1 would be rise in new infections would be reduced by 53\%
relative to the scenario without vaccinations, rapid tests, or seasonality.
